Variational Monte Carlo on bosonic systems

### 2018-03-24 project_1/article/article.tex
Wrote about importance sampling results.

>>>>

	\begin{table}
		\caption{Importance sampled simulations of $n=10$ particles in $d=3$ dimensions. Average acceptance
			ratios and standard deviations for eleven alpha values between $0.3$ and $0.7$.}
		\centering
			\begin{ruledtabular}
				\begin{tabular}{cccc}
				Time step & $\bar{\sigma}_b$ & $\bar{A}$ & $\expval{E}\left(\alpha = \frac{1}{2}\right)$ \\ \hline
				$2^{+3}$ & 0.09363 & 0.00531 & 15.000 \\
				$2^{+2}$ & 0.01549  & 0.04123 & 15.000 \\
				$2^{+1}$ & 0.00706 & 0.21604 & 15.000 \\ 
				$2^{\ 0}$ & 0.00675 & 0.51030 & 15.000 \\
				$2^{-1}$ & 0.00932 & 0.73779 & 15.000 \\
				$2^{-2}$ & 0.01578 & 0.86633 & 15.000 \\
				$2^{-3}$ & 0.02723 & 0.93305 & 15.000 \\
				$2^{-4}$ & 0.05016 & 0.96654 & 15.000 \\
				$2^{-5}$ & 0.08474 & 0.98316 & 15.000 \\
				$2^{-6}$ & 0.11555 & 0.99174 & 15.000 \\
				$2^{-7}$ & 0.17070 & 0.99612 & 15.000 \\
				\end{tabular}
			\end{ruledtabular}
			\label{tab:imp_time_step}
	\end{table}

	\autoref{tab:imp_time_step} shows the standard deviations and acceptance ratios for different time steps. The
	simulations in this tabel are from the same span $\alpha \in [0.3, 07]$ as in \autoref{tab:1D1N_analytic} and
	\autoref{tab:1D1N_numeric}. The optimum energies for $\alpha = \frac{1}{2}$ gives the same result for importance
	sampling as for the naïve way of sampling. Notice that by lowering the time step, the uncertainty starts to decrease
	and then starts to increase again. Moreover, the acceptance ratios increases as the time step decreases.
